Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-02 thesis/acm/paper.tex
Moar changes

%Interviews !!!improve later
After the initial source code inspection had been performed, interviews were conducted. The main purpose of these was to validate our findings during the code inspection with the designers of the APIs. Furthermore, the interviews were conducted to provide additional insight into decisions and motives behind changes that might have been overlooked during the code inspection. The final reason for interviewing the designers of the APIs was to provide further insight of the users of the API.

@@

@@

Each change between versions has been identified and grouped into three particular categories reflecting what kind of change they were; New, Modified, Removed and General Trends. Each section introduces the change and then discusses what the changes entailed, how we perceived them in relation to the twelve maintenance types, what our interviewee said about the changes and finally how the interviewees views of the changes relate to the maintenance categories. Each change was given a main category of maintenance and a subcategory if appropriate. This information will be used to answer \textbf{RQ1} and \textbf{RQ1.1}.

@@

See if our numbers match up with previous studies who said roughly 70\% of changes to an API were refactorings. That number is a little high in our case, but it's close!

RQ1.1
RQ2
What this means for industry:
	Greater emphasis should be placed upon communicating with the end users / application developers. APIs should be made with maintainability and extendibility in mind as they seem to be what changes the most between versions.

	Obvious benefit for Axis is that the more features == higher value for their camera. If they have many applications being developed by parters (In part due to the fact they have added more features to the camera API) then the value of their hardware and software will increase. This is probably the case for many other APIs but would need to be studied in some detail to determine the truth behind the statement.

What this means for academia

>>>>

%Interviews !!!improve later
After the initial source code inspection had been performed, interviews were conducted. The main purpose of these was to validate our findings during the code inspection with the designers of the APIs. Furthermore, the interviews were conducted to provide additional insight into decisions and motives behind changes that might have been overlooked during the code inspection. The final reason for interviewing the designers of the APIs was to provide further insight of the users of the API and how their decisions, needs and requirements have affected the development of the API.

@@

%Another threat was we were reliant upon being given documentation and code. I.e. they might not give us everything, leave stuff out, ignore things etc.

@@

Each change between versions has been identified and grouped into four particular categories reflecting what kind of change they were; New, Modified, Removed and General Trends. Each section introduces the change and then discusses what the changes entailed, how we perceived them in relation to the twelve maintenance types, what our interviewee said about the changes and finally how the interviewees views of the changes relate to the maintenance categories. Each change was given a main category of maintenance and a subcategory if appropriate. This information will be used to answer \textbf{RQ1} and \textbf{RQ1.1}.

@@

%See if our numbers match up with previous studies who said roughly 70\% of changes to an API were refactorings. That number is a little high in our case, but it's close!

RQ1.1 - To what extent can we reverse engineer API change decisions?
Roughly 78\% of our categorisation matched the actual categorisation of the changes. While it is true that we did not manage to successfully categorise every single change, we did categorise a high enough percentage to form a solid conclusion; it is possible to reverse engineer the majority of change decisions using this categorisation technique.

For future studies, this technique could be improved by performing more actions along side the code review. For example, having access to commit logs, design meetings and other such documentation would allow a much more thorough determination of intents to be performed.

RQ2
What this means for industry:
	Greater emphasis should be placed upon communicating with the end users / application developers. APIs should be made with maintainability and extendibility in mind as they seem to be what changes the most between versions.

	Obvious benefit for Axis is that the more features == more applications == higher value for their camera. If they have many applications being developed by partners (In part due to the fact they have added more features to the camera API) then the value of their hardware and software will increase. This is probably the case for many other APIs but would need to be studied in some detail to determine the truth behind the statement.

What this means for academia:
